\bf An Examination of Sport Climbing Competition Format and Scoring System

### 2021-07-29 manuscript/Rmd/draft.Rmd

The manuscript is outlined as follows. We first begin with some descriptions of the data and methods in Section 2. Our analyses and results are then presented in Sections 3 and 4. Finally, in Section 5, we summarize up of main findings and give a discussion to close out the paper.

@@

Table 1 and Figure 1 are numerical and visual summaries of climbing total score obtained from our simulated data for the qualification round.

@@

@@

@@

Corr

Drop 1

@@

## Speed climbing vs lead and bouldering

@@

## Drop and re-rank

@@

```{r, fig.cap = "This figure shows the rankings of the Men's Sport Climbing Final at the 2018 Youth Olympics. Each panel represents the dropped rank, with 0 being the original final standings. The cases where a change in ordering happened are highlighted.", fig.width = 7}
drop_rerank(mf) %>% 
  mutate(last = fct_reorder(last, -rank),
         rank = as.factor(rank),
         rank_change = ifelse(
           rank_drop %in% c(0, 4) | 
             rank_drop == 1 & rank %in% 4:5 |
              rank_drop == 2 & rank %in% c(1, 5) |
                rank_drop %in% c(3, 5) & rank %in% c(1, 2, 5) |
                  rank_drop == 6 & rank %in% 1:3, 
           "no", "yes")) %>% 
  ggplot(aes(x = last, y = total, fill = rank_change)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = rank), hjust = -0.2, size = 3) +
  coord_flip() +
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf),
            data = ~ filter(., rank_drop %in% c(1, 2, 3, 5, 6)), 
            color = "black", size = 1.5, fill = NA, inherit.aes = FALSE) +
  facet_wrap(~ rank_drop, nrow = 2) +
  expand_limits(y = 102, x = 0:7) +
  scale_fill_manual(values = c("grey", "chocolate")) +
  labs(y = "Score",
       x = "Climber") +
  theme_minimal() +
  theme(axis.ticks = element_blank(),
        panel.grid.minor = element_blank())
```

```{r, fig.cap = "This figure shows the final rankings of 2018 Youth Olympics Women's Final. Each panel represents the dropped rank, with 0 being the original final standings. The cases where a change in ordering happened are highlighted.", fig.width = 7}
drop_rerank(wf) %>% 
  mutate(last = fct_reorder(last, -rank),
         rank = as.factor(rank),
         rank_change = ifelse(
           rank_drop %in% c(0, 1, 4, 6) |
             rank_drop == 2 & rank %in% 1:3 |
              rank_drop == 3 & rank %in% c(1, 4, 5) |
                rank_drop == 5 & rank %in% c(1, 5),
           "no", "yes")) %>%
  ggplot(aes(x = last, y = total, fill = rank_change)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = rank), hjust = -0.2, size = 3) +
  coord_flip() +
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf),
            data = ~ filter(., rank_drop %in% c(2, 3, 5)), 
            color = "black", size = 1.5, fill = NA, inherit.aes = FALSE) +
  facet_wrap(~ rank_drop, nrow = 2, ncol = 4) +
  expand_limits(y = 62, x = 0:7) +
  scale_fill_manual(values = c("grey", "chocolate")) +
  labs(y = "Score",
       x = "Climber") +
  theme_minimal() +
  theme(axis.ticks = element_blank(),
        panel.grid.minor = element_blank())
```

>>>>

The manuscript is outlined as follows. We first begin with some descriptions of the data and methods in Section 2. Our analyses and results are then presented in Sections 3 and 4. Finally, in Section 5, we summarize up our main findings and provide a discussion to close out the paper.

@@

Table 1 and Figure 1 are numerical and visual summaries of climbing total score obtained from our simulated data for the qualification and final rounds.

@@

## Uniform Ranks

@@

## Leave-one-climber-out

6!

@@

@@

## Correlations

@@

## Leave-one-climber-out Analysis

@@

```{r}
mf_gg <- drop_rerank(mf) %>% 
  mutate(last = fct_reorder(last, -rank),
         rank = as.factor(rank),
         rank_change = ifelse(
           rank_drop %in% c(0, 4) | 
             rank_drop == 1 & rank %in% 4:5 |
              rank_drop == 2 & rank %in% c(1, 5) |
                rank_drop %in% c(3, 5) & rank %in% c(1, 2, 5) |
                  rank_drop == 6 & rank %in% 1:3, 
           "no", "yes")) %>% 
  ggplot(aes(x = last, y = total, fill = rank_change)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = rank), hjust = -0.2, size = 3) +
  coord_flip() +
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf),
            data = ~ filter(., rank_drop %in% c(1, 2, 3, 5, 6)), 
            color = "black", size = 1.5, fill = NA, inherit.aes = FALSE) +
  facet_wrap(~ rank_drop, nrow = 2) +
  expand_limits(y = 102, x = 0:7) +
  scale_fill_manual(values = c("grey", "chocolate")) +
  labs(x = "Men", y = "") +
  theme_minimal() +
  theme(axis.ticks = element_blank(),
        panel.grid.minor = element_blank())

wf_gg <- drop_rerank(wf) %>% 
  mutate(last = fct_reorder(last, -rank),
         rank = as.factor(rank),
         rank_change = ifelse(
           rank_drop %in% c(0, 1, 4, 6) |
             rank_drop == 2 & rank %in% 1:3 |
              rank_drop == 3 & rank %in% c(1, 4, 5) |
                rank_drop == 5 & rank %in% c(1, 5),
           "no", "yes")) %>%
  ggplot(aes(x = last, y = total, fill = rank_change)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = rank), hjust = -0.2, size = 3) +
  coord_flip() +
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf),
            data = ~ filter(., rank_drop %in% c(2, 3, 5)), 
            color = "black", size = 1.5, fill = NA, inherit.aes = FALSE) +
  facet_wrap(~ rank_drop, nrow = 2, ncol = 4) +
  expand_limits(y = 62, x = 0:7) +
  scale_fill_manual(values = c("grey", "chocolate")) +
  labs(y = "\nScore", x = "Women") +
  theme_minimal() +
  theme(axis.ticks = element_blank(),
        panel.grid.minor = element_blank())
```

```{r, fig.cap = "This figure illustrates the changes to the final rankings of the 2018 Youth Olympics Men's and Women's Finals when we leave out a single climber. For each gender competition, each panel represents the rank of the drop-out athlete, with 0 being the original final results. Each case with a change in rank orderings is highlighted by a black panel border, and any player with a rank change is represented by a red-filled bar", fig.width = 6.5, fig.height = 7.5}
library(patchwork)
mf_gg + wf_gg +
  plot_layout(nrow = 2)
```

### 2021-07-29 manuscript/Rmd/draft.tex
Update Rmd

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Histogram of simulated scores for qualification and final
rounds}
\end{figure}

@@

@@

@@

Corr

Drop 1

\hypertarget{speed-climbing-vs-lead-and-bouldering}{%
\subsection{Speed climbing vs lead and
bouldering}\label{speed-climbing-vs-lead-and-bouldering}}

@@

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{Kendall's rank correlations - 2018 World Championship, Women's
Qualification}
\end{figure}

\hypertarget{drop-and-re-rank}{%
\subsection{Drop and re-rank}\label{drop-and-re-rank}}

@@

The cases where someone behind you drops out and your ranking changes.

Example from 2018 youth, women's final dropping ranks 3 and 5 change the
medalist order

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{This figure shows the rankings of the Men's Sport Climbing
Final at the 2018 Youth Olympics. Each panel represents the dropped
rank, with 0 being the original final standings. The cases where a
change in ordering happened are highlighted.}
\end{figure}

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{This figure shows the final rankings of 2018 Youth Olympics
Women's Final. Each panel represents the dropped rank, with 0 being the
original final standings. The cases where a change in ordering happened
are highlighted.}
\end{figure}

>>>>

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\usepackage{caption}
\captionsetup[table]{skip=3pt}
\usepackage{float}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\begin{figure}[H]
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Histogram of simulated scores for qualification and final
rounds}
\end{figure}

@@

\hypertarget{uniform-ranks}{%
\subsection{Uniform Ranks}\label{uniform-ranks}}

@@

\hypertarget{leave-one-climber-out}{%
\subsection{Leave-one-climber-out}\label{leave-one-climber-out}}

6!

@@

\hypertarget{correlations}{%
\subsection{Correlations}\label{correlations}}

@@

\begin{figure}[H]
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{Kendall's rank correlations - 2018 World Championship, Women's
Qualification}
\end{figure}

\hypertarget{leave-one-climber-out-analysis}{%
\subsection{Leave-one-climber-out
Analysis}\label{leave-one-climber-out-analysis}}

@@

The cases where someone behind you drops out and your ranking changes.
Example from 2018 youth, women's final dropping ranks 3 and 5 change the
medalist order

\begin{figure}[H]
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{This figure illustrates the changes to the final rankings of
the 2018 Youth Olympics Men's and Women's Finals when we leave out a
single climber. For each gender competition, each panel represents the
rank of the drop-out athlete, with 0 being the original final results.
Each case with a change in rank orderings is highlighted by a black
panel border, and any player with a rank change is represented by a
red-filled bar}
\end{figure}
